---
title: "STA426_Week01"
output: html_document
---

# Exercise 01

Create an HTML document that samples 100 values from a log-normal distribution (say, mu=1, sigma=.25); create a histogram of the distribution and the distribution on the log scale; report the mean and variance of the sample in line in the text. In general, do not just dump the R code and plots in the HTML document; break your exercises into sections with headings, add some text and make it readable.

## 1. Sampling from log-normal distribution

```{r}
# sampling-parameters
set.seed(1)
mu <- 1
sigma <- 0.25
n<-100
sample <- rlnorm(n, meanlog = mu, sdlog = sigma)
```

## 2. Histogram

```{r}
# plotting
par(mfrow = c(2,1))
hist(sample, freq=F, main = "Histogram")
hist(log(sample), freq=F,, main = "Histogram Log-scale")
```

## 3. Calculation of mean and variance

```{r}
sample_mean <- mean(sample)
sample_var <- var(sample)

log_sample_mean <- mean(log(sample))
log_sample_var <- var(log(sample))
```

The calculated mean of the sample is `r sample_mean` and the calculated variance is `r sample_var`.

The mean and variance of the log-transformed sample is `r log_sample_mean` and `r log_sample_mean` respectively.
